---
title: "ClassifyMethod_EZ"
author: "Eleanor Zhang"
date: "5/9/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 7,fig.asp = .7,out.width = "90%",
                      message = FALSE, warning = FALSE)
library(tidyverse)
library(caret)
library(boot)
library(corrplot)
library(glmnet)
library(splines)
library(mgcv)
library(RColorBrewer)
library(MASS) # contain data
library(mlbench) 
library(pROC) # generate ROC curve
library(AppliedPredictiveModeling)
library(ggpubr)
theme_set(theme_classic())
```

## Data 

Binary outcome: high rating = 1
```{r}
apple <- read_csv("./data/AppleStore.csv") %>%
  janitor::clean_names() %>%
  dplyr::select(-c(x1, id, track_name, currency, ver)) %>%
  mutate(size_bytes = round(size_bytes * 1e-6),
         cont_rating = factor(cont_rating, levels = c("4+", "9+","12+","17+")),
         user_rating = factor(ifelse(user_rating >= 4, "high", "med.low"), levels = c("med.low","high"))) %>%
  rename(size_megabytes = size_bytes) %>%
  filter(rating_count_tot != 0,
         user_rating_ver != 0) %>% #Remove apps with no user rating
  mutate(prime_genre = as.integer(ifelse(prime_genre == "Games", 1, 0))) %>% 
  dplyr::select(-rating_count_tot, -rating_count_ver, -vpp_lic) #vpp_lic has nearzero variance

str(apple)
contrasts(apple$user_rating)
table(apple$user_rating)
```

split data into train and test
```{r}
set.seed(1234)
#Split data to traning and testing
trRows = createDataPartition(apple$user_rating,
                             p = .75,
                             list = FALSE)
train_data = apple[trRows,]
test_data = apple[-trRows,]
#in matrix form
x_train = model.matrix(user_rating~., train_data)[,-1] 
y_train = train_data$user_rating
x_test = model.matrix(user_rating~., test_data)[,-1] 
y_test = test_data$user_rating

ctrl1 = trainControl(method = "cv", number = 10)
```

continous outcome
```{r}
apple1 <- read_csv("./data/AppleStore.csv") %>%
  janitor::clean_names() %>%
  dplyr::select(-c(x1, id, track_name, currency, ver)) %>%
  mutate(size_bytes = round(size_bytes * 1e-6),
         cont_rating = factor(cont_rating, levels = c("4+", "9+","12+","17+")))%>%
  rename(size_megabytes = size_bytes) %>%
  filter(rating_count_tot != 0,
         user_rating_ver != 0) %>% #Remove apps with no user rating
  mutate(prime_genre = as.integer(ifelse(prime_genre == "Games", 1, 0))) %>% 
  dplyr::select(-rating_count_tot, -rating_count_ver, -vpp_lic) #vpp_lic has nearzero variance

train_data1 = apple1[trRows,]
test_data1 = apple1[-trRows,]
#in matrix form
x_train1 = model.matrix(user_rating~., train_data1)[,-1] 
y_train1 = train_data1$user_rating
x_test1 = model.matrix(user_rating~., test_data1)[,-1] 
y_test1 = test_data1$user_rating
```

## Data descriptions and EDA

size megabytes is right skewed, mostly less than 1000 mb;  
price is right skewed, most less than $10;  
overall user rating is left skewed; recode into binary variable as either high rating(>= 4) or low (<4) user rating of current version

continous
```{r}
transparentTheme(trans = .4)
featurePlot(x = apple[, c(1,2,4,7,8,9)], # all features are numeric
            y = factor(apple$user_rating), # binary variable
            scales = list(x = list(relation="free"), 
                        y = list(relation="free")), # set both x and y scales to be free
            plot = "density", # density plot for each variable; 
            pch = "|",  # set the marker
            auto.key = list(columns = 2))
```

categorical
```{r}
# aggregate(user_rating ~ cont_rating + prime_genre, data = apple, mean)
apple %>% mutate(user_rating = factor(user_rating),
                 prime_genre = factor(prime_genre)) %>% 
  group_by(user_rating, prime_genre, cont_rating) %>% 
  summarize(n = n()) %>% 
  ggplot(aes(x = cont_rating, y = n))+
  geom_bar(
    aes(fill = factor(prime_genre)), stat = "identity", color = "white",
    position = position_dodge(0.9)
    )+
  facet_wrap(~user_rating) + 
  fill_palette("jco") + 
  labs(title="frequency of user rating category by content level and prime genre", 
       subtitle = "0: medium/low rating, 1: high rating",
         x="Content rating level")
```


## Methods

```{r}
library(rpart) # for recursive partition (CART: Classfification and Regression Tree)
library(rpart.plot) # better tool to visualze CART tree
library(party) # conditional inference tree (stopping criterion is based on permutation test; problem of early stoppoing)
library(partykit) # visualize party object
library(randomForest) # random Forest; could be slow
library(ranger) # C++ improvement on randomForest; much faster for tuning paremeter
library(gbm) # gradient boosting machine (boosting)
library(plotmo) 
library(pdp) # create partial dependence plot
library(lime)
```

### CART: regression tree 
use only caret package to tune

```{r}
ctrl1 = trainControl(method = "cv", number = 10) # very slow
```

Tune Cp: best = 0.002
```{r}
set.seed(1234)
# tune over cp, method = "rpart"
rpart.fit <- train(user_rating~., train_data1, 
                   method = "rpart",
                   tuneGrid = data.frame(cp = exp(seq(-10,-4, length = 20))), # try many values here
                   trControl = ctrl1)
ggplot(rpart.fit, highlight = TRUE)
rpart.fit$bestTune # 0.002
rpart.plot(rpart.fit$finalModel)
```

tune maximum depth : best = 5
```{r}
set.seed(1234)
rpart2.fit <- train(user_rating~., train_data1, 
                   method = "rpart2",
                   tuneGrid = data.frame(maxdepth = 1:10), 
                   trControl = ctrl1)
ggplot(rpart2.fit, highlight = TRUE)
rpart2.fit$bestTune # depth = 5
rpart.plot(rpart2.fit$finalModel)
```

### Conditional inference tree (regression)

stopping criterion is p value; at each step, the splitting rule is selected as the variable with strongest association with response. 
*  pros: Avoid variable selection bias towards predictors with many possible cut points; ensures the right size tree is grown without additional pruning or cross validation, 
*  cons: can stop early. 
Tune: `mincriterion` (1- p.value)  

```{r}
set.seed(1234)
ctree.fit <- train(user_rating~., train_data1, 
                   method = "ctree",
                   tuneGrid = data.frame(mincriterion = 1-exp(seq(-7, -2, length = 30))),
                   trControl = ctrl1)
ggplot(ctree.fit, highlight = TRUE)
ctree.fit$bestTune # 1 - p.value = 0.932
plot(ctree.fit$finalModel)
```


### CART: classfication tree 

use caret package only

Tune Cp
```{r}
ctrl2 <- trainControl(method = "cv",
                     summaryFunction = twoClassSummary, # use ROC curve as summary
                     classProbs = TRUE)

set.seed(1234)
rpart.fit.bin <- train(user_rating~., apple, 
                   subset = trRows,
                   method = "rpart",
                   tuneGrid = data.frame(cp = exp(seq(-6,-3, len = 30))), 
                   trControl = ctrl2,
                   metric = "ROC")

ggplot(rpart.fit.bin, highlight = TRUE)
rpart.fit.bin$bestTune # cp = 0.0037, treesize = 7
rpart.fit.bin$finalModel$cptable # look at the last row : treesize = nsplit + 1 = 6 + 1
rpart.plot(rpart.fit.bin$finalModel) 
```

### Conditional Inference tree (classifcation)

```{r}
set.seed(1234)
ctree.fit.bin <- train(user_rating~., apple, 
                   subset = trRows,
                   method = "ctree",
                   tuneGrid = data.frame(mincriterion = 1-exp(seq(-4, -1, length = 30))), # 1-alpha
                   metric = "ROC",
                   trControl = ctrl2)
ggplot(ctree.fit.bin, highlight = TRUE)
ctree.fit.bin$bestTune # 1- p.value = 0.894
plot(ctree.fit.bin$finalModel)
```

### predict on test data (regression)

```{r}
rpart.pred <- predict.train(rpart.fit, newdata = apple1[-trRows,]) # CART tree: Cp
rpart.pred2 <- predict.train(rpart2.fit, newdata = apple1[-trRows,]) # CART tree: maximum depth
ctree.pred <- predict.train(ctree.fit, newdata = apple1[-trRows,]) # ctree
```


### predict on test data (classification)

```{r}
# predict on further tuning on cost complexity
rpart.pred.bin <- predict(rpart.fit.bin, newdata = apple[-trRows,], 
                      type = "prob")[,1] # probability
# predict on ctree
rpartc.pred.bin <- predict(ctree.fit.bin, newdata = apple[-trRows,],
                       type = "prob")[,1]
```


