---
title: "Finalproject_Ma"
author: "Mengran Ma"
date: "5/10/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 7,fig.asp = .7,out.width = "90%",
                      message = FALSE, warning = FALSE)
library(tidyverse)
library(ggridges)
library(caret)
library(boot)
library(pls)
library(glmnet)
library(splines)
library(mgcv)
library(MASS)
library(pROC)
library(GGally)
library(RColorBrewer)
library(randomForest) 
library(ranger)
theme_set(theme_classic())
library(gbm)
# parallel processing with caret
library(doParallel)
cluster <- makePSOCKcluster(10)
registerDoParallel(cluster)

```

## Data 

Binary outcome
```{r}
apple <- read_csv("./data/AppleStore.csv") %>%
  janitor::clean_names() %>%
  dplyr::select(-c(x1, id, track_name, currency, ver)) %>%
  mutate(size_bytes = round(size_bytes * 1e-6),
         cont_rating = factor(cont_rating, levels = c("4+", "9+","12+","17+")),
         user_rating = ifelse(user_rating >= 4, 1, 0)) %>%
  rename(size_megabytes = size_bytes) %>%
  filter(rating_count_tot != 0,
         user_rating_ver != 0) %>% #Remove apps with no user rating
  mutate(prime_genre = as.integer(ifelse(prime_genre == "Games", 1, 0)),
         user_rating = as.numeric(user_rating)) %>% 
  dplyr::select(-rating_count_tot, -rating_count_ver, -vpp_lic) #vpp_lic has nearzero variance

str(apple)
table(apple$user_rating)
```

split data into train and test
```{r}
set.seed(1234)
#Split data to traning and testing
trRows = createDataPartition(apple$user_rating,
                             p = .75,
                             list = FALSE)
train_data = apple[trRows,]
test_data = apple[-trRows,]
#in matrix form
x_train = model.matrix(user_rating~., train_data)[,-1] 
y_train = train_data$user_rating
x_test = model.matrix(user_rating~., test_data)[,-1] 
y_test = test_data$user_rating

ctrl1 = trainControl(method = "cv", number = 10)
```

continous outcome
```{r}
apple1 <- read_csv("./data/AppleStore.csv") %>%
  janitor::clean_names() %>%
  dplyr::select(-c(x1, id, track_name, currency, ver)) %>%
  mutate(size_bytes = round(size_bytes * 1e-6),
         cont_rating = factor(cont_rating, levels = c("4+", "9+","12+","17+")))%>%
  rename(size_megabytes = size_bytes) %>%
  filter(rating_count_tot != 0,
         user_rating_ver != 0) %>% #Remove apps with no user rating
  mutate(prime_genre = as.integer(ifelse(prime_genre == "Games", 1, 0))) %>% 
  dplyr::select(-rating_count_tot, -rating_count_ver, -vpp_lic) #vpp_lic has nearzero variance

str(apple1)

train_data1 = apple1[trRows,]
test_data1 = apple1[-trRows,]
#in matrix form
x_train1 = model.matrix(user_rating~., train_data1)[,-1] 
y_train1 = train_data1$user_rating
x_test1 = model.matrix(user_rating~., test_data1)[,-1] 
y_test1 = test_data1$user_rating
```

## Data descriptions

size megabytes is right skewed, mostly less than 1000 mb;  
price is right skewed, most less than $10;  
overall user rating is left skewed; recode into binary variable as either high rating(>= 4) or low (<4) user rating of current version

#Bagging
```{r}
bag.grid <- expand.grid(mtry = 8, splitrule = "gini", min.node.size = 1:6) 
set.seed(1234)

bag.fit <- train(user_rating~., train_data2, method = "ranger", tuneGrid = bag.grid, trControl = ctrl2)
ggplot(bag.fit, highlight = TRUE)

bag.fit$bestTune
```

```{r}
bag.grid2 <- expand.grid(mtry = 8, splitrule = "variance", min.node.size = 1:150) 
set.seed(1234)

bag.fit2 <- train(user_rating~., train_data1, method = "ranger", tuneGrid = bag.grid2, trControl = ctrl1)
ggplot(bag.fit2, highlight = TRUE)

bag.fit2$bestTune
```

```{r}
set.seed(1234)
bagging <- ranger(user_rating~., train_data, mtry = 8, min.node.size = 260) 
bagging.per <- ranger(user_rating~., train_data, 
                      mtry = 8, 
                      splitrule = "variance",
                      min.node.size = 260,
                      importance = "permutation",
                      scale.permutation.importance = TRUE) # better to standardize importance

barplot(sort(ranger::importance(bagging.per), decreasing = FALSE),
        las = 2, horiz = TRUE, cex.names = 0.7, main = "Permutation OOB-Binary Outcome", 
        col = colorRampPalette(colors = c("darkred","white","darkblue"))(8))

set.seed(1234)
bagging.impurity <- ranger(user_rating~., train_data,
                        mtry = 8, splitrule = "variance",
                        min.node.size = 260,
                        importance = "impurity")
barplot(sort(ranger::importance(bagging.impurity), decreasing = FALSE),
        las = 2, horiz = TRUE, cex.names = 0.7, main = "Impurity (RSS)-Binary Outcome",
        col = colorRampPalette(colors = c("darkred","white","darkblue"))(8))
```

```{r}
set.seed(1234)
bagging2 <- ranger(user_rating~., train_data1, mtry = 8, min.node.size = 81) 
bagging.per2 <- ranger(user_rating~., train_data1, 
                      mtry = 8, 
                      splitrule = "variance",
                      min.node.size = 81,
                      importance = "permutation",
                      scale.permutation.importance = TRUE) # better to standardize importance

barplot(sort(ranger::importance(bagging.per), decreasing = FALSE),
        las = 2, horiz = TRUE, cex.names = 0.7, main = "Permutation OOB-Continuous Outcome", 
        col = colorRampPalette(colors = c("darkred","white","darkblue"))(8))

set.seed(1234)
bagging.impurity2 <- ranger(user_rating~., train_data1,
                        mtry = 8, splitrule = "variance",
                        min.node.size = 81,
                        importance = "impurity")
barplot(sort(ranger::importance(bagging.impurity), decreasing = FALSE),
        las = 2, horiz = TRUE, cex.names = 0.7, main = "Impurity (RSS)-Continuous Outcome",
        col = colorRampPalette(colors = c("darkred","white","darkblue"))(8))
```


#Random Forest
```{r}
# Try more if possible
rf.grid <- expand.grid(mtry = 1:8,
                       splitrule = "gini",
                       min.node.size = 1:6)
set.seed(1234)
rf.fit <- train(user_rating~., train_data2,
                method = "ranger",
                tuneGrid = rf.grid,
                metric = "ROC",
                trControl = ctrl2)

ggplot(rf.fit, highlight = TRUE)
rf.fit$bestTune
```

```{r}
# Try more if possible
rf.grid2 <- expand.grid(mtry = 1:8,
                       splitrule = "variance",
                       min.node.size = 1:6)
set.seed(1234)
rf.fit2 <- train(user_rating~., train_data1,
                method = "ranger",
                tuneGrid = rf.grid2,
                trControl = ctrl1)

ggplot(rf.fit2, highlight = TRUE)
rf.fit2$bestTune
```

```{r, fig.width=10, dpi=300}
set.seed(1234)
rf.final.per <- ranger(user_rating~., train_data2,
                        mtry = 2, splitrule = "gini",
                        min.node.size = 6,
                        importance = "permutation",
                        scale.permutation.importance = TRUE)
barplot(sort(ranger::importance(rf.final.per), decreasing = FALSE),
        las = 2, horiz = TRUE, cex.names = 0.7, main = "Permutation OOB for Binary outcome/response",
        col = colorRampPalette(colors = c("darkred","white","darkblue"))(8))

set.seed(1234)
rf.final.imp <- ranger(user_rating~., train_data2,
                        mtry = 2, splitrule = "gini",
                        min.node.size = 6,
                        importance = "impurity")
barplot(sort(ranger::importance(rf.final.imp), decreasing = FALSE),
        las = 2, horiz = TRUE, cex.names = 0.7, main = "Impurity (RSS) for Binary outcome/response",
        col = colorRampPalette(colors = c("darkred","white","darkblue"))(8))
```

```{r, fig.width=1, dpi=300}
set.seed(1234)
rf2.final.per2 <- ranger(user_rating~., apple1,
                         mtry = 3, splitrule = "variance",
                         min.node.size = 5,
                         importance = "permutation",
                         scale.permutation.importance = TRUE)
barplot(sort(ranger::importance(rf2.final.per2), decreasing = FALSE),
        las = 2, horiz = TRUE, cex.names = 0.7, main = "Permutation OOB for Contious outcome/response",
        col = colorRampPalette(colors = c("darkred","white","darkblue"))(8))

set.seed(1234)
rf2.final.imp2 <- ranger(user_rating~., train_data1,
                        mtry = 3, splitrule = "variance",
                        min.node.size = 5,
                        importance = "impurity")
barplot(sort(ranger::importance(rf2.final.imp2), decreasing = FALSE),
        las = 2, horiz = TRUE, cex.names = 0.7, main = "Impurity (RSS) for Continuous outcome/response",
        col = colorRampPalette(colors = c("darkred","white","darkblue"))(8))
```


#Boosting
```{r}
set.seed(1234)
bst <- gbm(user_rating~., train_data,
           distribution = "adaboost",
           n.trees = 3000,
           interaction.depth = 2,
           shrinkage = 0.005,
           cv.folds = 10)
nt <- gbm.perf(bst, method = "cv")
nt
```

```{r}
set.seed(1234)
bst <- gbm(user_rating~., train_data1,
           distribution = "gaussian", # use RSS loss function (l2 method)
           n.trees = 5000, # number of trees (B) 
           interaction.depth = 1, # depth of tree (d) 
           shrinkage = 0.005, # learnng rate lambda 
           cv.folds = 10)
gbm.perf(bst, method = "cv")
```

```{r}

# Try more
gbm.grid <- expand.grid(n.trees = c(2000, 3000, 4000), interaction.depth = 1:10,
                        shrinkage = c(0.001,0.003,0.005), n.minobsinnode = 1)
set.seed(1234)
gbm.fit <- train(user_rating~., train_data2,
                 method = "gbm",
                 distribution = "bernoulli",
                 tuneGrid = gbm.grid,
                 trControl = ctrl2,
                 metric = "ROC",
                 verbose = FALSE)
ggplot(gbm.fit, highlight = TRUE)
gbm.fit$bestTune

summary(gbm.fit$finalModel, las = 2, cBars = 8, cex.names = 0.8)
```

```{r}

# Try more
gbm.grid3 <- expand.grid(n.trees = c(2000, 3000, 4000), interaction.depth = 1:10,
                        shrinkage = c(0.001,0.003,0.005), n.minobsinnode = 1)
set.seed(1234)
gbm.fit3 <- train(user_rating~., train_data2,
                 method = "gbm",
                 distribution = "adaboost",
                 tuneGrid = gbm.grid3,
                 trControl = ctrl2,
                 metric = "ROC",
                 verbose = FALSE)
ggplot(gbm.fit3, highlight = TRUE)
gbm.fit3$bestTune

summary(gbm.fit3$finalModel, las = 2, cBars = 8, cex.names = 0.8)
```

```{r}
# Try more
gbm.grid2 <- expand.grid(n.trees = c(2000, 3000, 4000), interaction.depth = 1:10,
                        shrinkage = c(0.001,0.003,0.005), n.minobsinnode = 1)
set.seed(1234)
gbm.fit2 <- train(user_rating~., train_data1,
                 method = "gbm",
                 tuneGrid = gbm.grid2,
                 trControl = ctrl1,
                 verbose = FALSE)
ggplot(gbm.fit2, highlight = TRUE)
gbm.fit2$bestTune

summary(gbm.fit2$finalModel, las = 2, cBars = 8, cex.names = 0.8)
```



```{r, echo=F}
stopCluster(cluster)
```

## Data 

Binary outcome: high rating = 1
```{r}
apple2 <- read_csv("./data/AppleStore.csv") %>%
  janitor::clean_names() %>%
  dplyr::select(-c(x1, id, track_name, currency, ver)) %>%
  mutate(size_bytes = round(size_bytes * 1e-6),
         cont_rating = factor(cont_rating, levels = c("4+", "9+","12+","17+")),
         user_rating = factor(ifelse(user_rating >= 4, "high", "med.low"), levels = c("med.low","high"))) %>%
  rename(size_megabytes = size_bytes) %>%
  filter(rating_count_tot != 0,
         user_rating_ver != 0) %>% #Remove apps with no user rating
  mutate(prime_genre = as.integer(ifelse(prime_genre == "Games", 1, 0))) %>% 
  dplyr::select(-rating_count_tot, -rating_count_ver, -vpp_lic) #vpp_lic has nearzero variance

str(apple2)
contrasts(apple2$user_rating)
table(apple2$user_rating)
```

split data into train and test
```{r}
set.seed(1234)
#Split data to traning and testing
trRows = createDataPartition(apple2$user_rating,
                             p = .75,
                             list = FALSE)
train_data2 = apple2[trRows,]
test_data2 = apple2[-trRows,]
#in matrix form
x_train = model.matrix(user_rating~., train_data2)[,-1] 
y_train = train_data2$user_rating
x_test = model.matrix(user_rating~., test_data2)[,-1] 
y_test = test_data2$user_rating

ctrl1 = trainControl(method = "cv", number = 10)
```

continous outcome
```{r}
apple21 <- read_csv("./data/AppleStore.csv") %>%
  janitor::clean_names() %>%
  dplyr::select(-c(x1, id, track_name, currency, ver)) %>%
  mutate(size_bytes = round(size_bytes * 1e-6),
         cont_rating = factor(cont_rating, levels = c("4+", "9+","12+","17+")))%>%
  rename(size_megabytes = size_bytes) %>%
  filter(rating_count_tot != 0,
         user_rating_ver != 0) %>% #Remove apps with no user rating
  mutate(prime_genre = as.integer(ifelse(prime_genre == "Games", 1, 0))) %>% 
  dplyr::select(-rating_count_tot, -rating_count_ver, -vpp_lic) #vpp_lic has nearzero variance

train_data21 = apple21[trRows,]
test_data21 = apple21[-trRows,]
#in matrix form
x_train1 = model.matrix(user_rating~., train_data21)[,-1] 
y_train1 = train_data21$user_rating
x_test1 = model.matrix(user_rating~., test_data21)[,-1] 
y_test1 = test_data21$user_rating
```



## Methods

```{r}
library(rpart) # for recursive partition (CART: Classfification and Regression Tree)
library(rpart.plot) # better tool to visualze CART tree
library(party) # conditional inference tree (stopping criterion is based on permutation test; problem of early stoppoing)
library(partykit) # visualize party object
library(randomForest) # random Forest; could be slow
library(ranger) # C++ improvement on randomForest; much faster for tuning paremeter
library(gbm) # gradient boosting machine (boosting)
library(plotmo) 
library(pdp) # create partial dependence plot
library(lime)
```

### CART: regression tree 
use only caret package to tune

```{r}
ctrl1 = trainControl(method = "cv", number = 10) # very slow
```

Tune Cp: best = 0.002
```{r}
set.seed(1234)
# tune over cp, method = "rpart"
rpart.fit <- train(user_rating~., train_data1, 
                   method = "rpart",
                   tuneGrid = data.frame(cp = exp(seq(-10,-4, length = 20))), # try many values here
                   trControl = ctrl1)
ggplot(rpart.fit, highlight = TRUE)
rpart.fit$bestTune # 0.002
rpart.plot(rpart.fit$finalModel)
```

tune maximum depth : best = 5
```{r}
set.seed(1234)
rpart2.fit <- train(user_rating~., train_data1, 
                   method = "rpart2",
                   tuneGrid = data.frame(maxdepth = 1:10), 
                   trControl = ctrl1)
ggplot(rpart2.fit, highlight = TRUE)
rpart2.fit$bestTune # depth = 5
rpart.plot(rpart2.fit$finalModel)
```

### Conditional inference tree (regression)

stopping criterion is p value; at each step, the splitting rule is selected as the variable with strongest association with response. 
*  pros: Avoid variable selection bias towards predictors with many possible cut points; ensures the right size tree is grown without additional pruning or cross validation, 
*  cons: can stop early. 
Tune: `mincriterion` (1- p.value)  

```{r}
set.seed(1234)
ctree.fit <- train(user_rating~., train_data1, 
                   method = "ctree",
                   tuneGrid = data.frame(mincriterion = 1-exp(seq(-7, -2, length = 30))),
                   trControl = ctrl1)
ggplot(ctree.fit, highlight = TRUE)
ctree.fit$bestTune # 1 - p.value = 0.932
plot(ctree.fit$finalModel)
```


### CART: classfication tree 

use caret package only

Tune Cp
```{r}
ctrl2 <- trainControl(method = "cv",
                     summaryFunction = twoClassSummary, # use ROC curve as summary
                     classProbs = TRUE)

set.seed(1234)
rpart.fit.bin <- train(user_rating~., apple2, 
                   subset = trRows,
                   method = "rpart",
                   tuneGrid = data.frame(cp = exp(seq(-6,-3, len = 30))), 
                   trControl = ctrl2,
                   metric = "ROC")

ggplot(rpart.fit.bin, highlight = TRUE)
rpart.fit.bin$bestTune # cp = 0.0037, treesize = 7
rpart.fit.bin$finalModel$cptable # look at the last row : treesize = nsplit + 1 = 6 + 1
rpart.plot(rpart.fit.bin$finalModel) 
```

### Conditional Inference tree (classifcation)

```{r}
set.seed(1234)
ctree.fit.bin <- train(user_rating~., apple2, 
                   subset = trRows,
                   method = "ctree",
                   tuneGrid = data.frame(mincriterion = 1-exp(seq(-4, -1, length = 30))), # 1-alpha
                   metric = "ROC",
                   trControl = ctrl2)
ggplot(ctree.fit.bin, highlight = TRUE)
ctree.fit.bin$bestTune # 1- p.value = 0.894
plot(ctree.fit.bin$finalModel)
```

### predict on test data (regression)

```{r}
rpart.pred <- predict.train(rpart.fit, newdata = apple21[-trRows,]) # CART tree: Cp
rpart.pred2 <- predict.train(rpart2.fit, newdata = apple21[-trRows,]) # CART tree: maximum depth
ctree.pred <- predict.train(ctree.fit, newdata = apple21[-trRows,]) # ctree
bag.pred <- predict.train(bag.fit, newdata = apple21[-trRows,]) # Bagging
rf.pred <- predict.train(rf.fit2, newdata = apple21[-trRows,]) # Random Forest
gbm.pred <- predict.train(gbm.fit2, newdata = apple21[-trRows,]) # Boosting
```

#Compare models:training error/RMSE comparison

```{r}
resamp2 <- resamples(list(rpart = rpart.fit, rpart2 = rpart.fit2,bag = bag.fit2, rf = rf.fit2, gbm = gbm.fit2)) 
summary(resamp2)
bwplot(resamp2, metric = "RMSE")
```

### predict on test data (classification)

```{r}
# predict on further tuning on cost complexity
rpart.pred.bin <- predict(rpart.fit.bin, newdata = apple2[-trRows,], 
                      type = "prob")[,1] # probability
# predict on ctree
rpartc.pred.bin <- predict(ctree.fit.bin, newdata = apple2[-trRows,],
                       type = "prob")[,1]
# predict on random forest
rf.pred.bin <- predict(rf.fit, newdata = apple2[-trRows,], 
                      type = "prob")[,1] # probability
# predict on Binomial loss boosting
gbm.pred.bin <- predict(gbm.fit, newdata = apple2[-trRows,],
                       type = "prob")[,1]

# predict on Ada boosting
gbm3.pred.bin <- predict(gbm.fit3, newdata = apple2[-trRows,],
                       type = "prob")[,1]
```

```{r}
roc.rpart <- roc(apple2$user_rating[-trRows], rpart.pred.bin) 
roc.rpartc <- roc(apple2$user_rating[-trRows], rpartc.pred.bin) 
roc.rf <- roc(apple2$user_rating[-trRows], rf.pred.bin) 
roc.gbm <- roc(apple2$user_rating[-trRows], gbm.pred.bin)
roc.gbm3 <- roc(apple2$user_rating[-trRows], gbm3.pred.bin) 

plot(roc.rpart)
plot(roc.rpartc, add = TRUE, col = 2) 
plot(roc.rf, add = TRUE, col = 3) 
plot(roc.gbm, add = TRUE, col = 4) 
plot(roc.gbm3, add = TRUE, col = 5)

auc <- c(roc.rpart$auc[1], roc.rpartc$auc[1], roc.rf$auc[1], roc.gbm$auc[1], roc.gbm3$auc[1])
modelNames <- c("rpart","ctree","rf","gbm","gbmA") 
legend("bottomright", legend = paste0(modelNames, ": ", round(auc,3)), col = 1:5, lwd = 2)
```

